---
title: "Homework 1"
author: "Liner Ge"
date: "2020/9/16"
output: github_document
---

This is my solution to hw1.
```{r}
library(tidyverse)
```

## Problem 1
Create a data frame with the specified elements.
```{r}
prob1_df=
  tibble(
    samp=rnorm(10),
    samp_gt_0=samp>0,
    char_vec=c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec=factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame.
```{r}
mean(pull(prob1_df,samp))
mean(pull(prob1_df,samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))
```
What works and what doesn't?
The mean function works for samp and samp_gt_0,because they are numbers. However, it doesn't work for char_vec or factor_vec, because they are not numeric or logical.

```{r, eval=FALSE}
as.numeric(pull(prob1_df,samp))
as.numeric(pull(prob1_df,samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))

as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
as.numeric(factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)
```
What happens and why?
The character cannot be converted to numeric. The factor is converted to numeric.
Does this help explain what happens when you try to take the mean?
Yes.

## Problem 2

Download a package. (This code wouldn't be executed.)
```{r, eval=FALSE}
install.packages("palmerpenguins")
```
Download a dataset.
```{r}
data("penguins", package = "palmerpenguins")
```
A short description of penguins
```{r}
penguins
nrow(penguins)
ncol(penguins)
mean(pull(penguins,flipper_length_mm),na.rm=T)
```
Make a scatterplot
```{r}
myplot.png=ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm,color=species))+geom_point()
myplot.png
ggsave("myplot.png",height=4, width=4)
```
