---
title: "Homework 1"
author: "Liner Ge"
date: "2020/9/16"
output: github_document
---

This is my solution to hw1.
```{r}
library(tidyverse)
```

# Problem 1
Create a data frame with the specified elements.
```{r}
prob1_df=
  tibble(
    samp=rnorm(10),
    samp_gt_0=samp>0,
    char_vec=c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec=factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame.
```{r}
mean(pull(prob1_df,samp))
mean(pull(prob1_df,samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))
```
## What works and what doesn't?

The mean function works for samp and samp_gt_0,because they are numbers. However, it doesn't work for char_vec or factor_vec, because they are not numeric or logical.


Apply the as.numeric function.(The output wouldn't be showed)
```{r, eval=FALSE}
as.numeric(pull(prob1_df,samp))
as.numeric(pull(prob1_df,samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))
```
```{r}
as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
as.numeric(factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)
```
## What happens and why?

The character cannot be converted to numeric. The factor is converted to numeric.

## Does this help explain what happens when you try to take the mean?

Yes.

# Problem 2

Download a dataset.
```{r}
data("penguins", package = "palmerpenguins")
```
## A short description of penguins

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` colums, and it includes variables -- `r names(penguins)`.The levels of species are:`r levels(pull(penguins,species))`; the levels of islands are:`r levels(pull(penguins,island))`; the levels of sex are:`r levels(pull(penguins,sex))`. The range of bill length is `r range(pull(penguins, bill_length_mm),na.rm=T)`mm; the range of bill depth is `r range(pull(penguins, bill_depth_mm),na.rm=T)`mm; the range of flipper length is `r range(pull(penguins, flipper_length_mm),na.rm=T)`mm; the range of body mass is`r range(pull(penguins, body_mass_g),na.rm=T)`g. The mean of flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm=T)`mm.


## Make a scatterplot
```{r}
myplot.png=ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm,color=species))+geom_point()
myplot.png
ggsave("myplot.png",height=4, width=4)
```
